---
title: "Group Presentation"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.height = 6, fig.width = 8)
```

```{r}
library(readit)
library(tidyverse)
cpgp <- readit("cpgp.csv")
library(rgdal)
```

```{r}
cpgp <- cpgp %>%
  mutate(pct = round((CPGP - Control) / Control * 100,1))
cpgp_td <- cpgp %>%
  gather(group, yield, CPGP:Control) 
```


```{r}
dry <- cpgp_td %>% filter(group == "Control", season == "dry")
```

## Option 1

* Bars are arranged in decreasing order of yield in areas not applied with carageenan.
* Two separate plots (by season).

```{r}
cpgp %>%
  filter(season == "dry") %>%
  mutate(province = reorder(province, -Control)) %>%
  gather(group, yield, CPGP:Control) %>%
  ggplot(aes(province, yield, fill = group)) +
  geom_col(position = position_dodge(), alpha = 0.7, color = "black") +
  scale_fill_grey(start = 0.2, end = .7) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  xlab("Province") +
  ylab("Yield (no. of sacks/ha)") +
  guides(fill=guide_legend(title="Treatment")) +
  ggtitle("Rice Yield by Province", subtitle = "Dry Season, 2018") +
  labs(caption = "Source: Field verification testing results of carageenan plant food supplement (CPGP), DOST-Region 2") 
```



```{r}
cpgp %>%
  filter(season == "dry") %>%
  mutate(province = reorder(province, -CPGP)) %>%
  gather(group, yield, CPGP:Control) %>%
  ggplot(aes(province, yield, fill = group)) +
  geom_col(position = position_dodge(), alpha = 0.7, color = "black") +
  scale_fill_grey(start = 0.2, end = .7) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  xlab("Province") +
  ylab("Yield (no. of sacks/ha)") +
  guides(fill=guide_legend(title="Treatment")) +
  ggtitle("Rice Yield by Province", subtitle = "Dry Season, 2018") +
  labs(caption = "Source: Field verification testing results of carageenan plant food supplement (CPGP), DOST-Region 2") 
```

## Option 2

* Bars are arranged in decreasing order of yield in areas applied with carageenan.
* Two separate plots (by season).

```{r}
cpgp %>%
  filter(season == "wet") %>%
  mutate(province = reorder(province, -Control)) %>%
  gather(group, yield, CPGP:Control) %>%
  ggplot(aes(province, yield, fill = group)) +
  geom_col(position = position_dodge(), alpha = 0.7, color = "black") +
  scale_fill_grey(start = 0.2, end = .7) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  xlab("Province") +
  ylab("Yield (no. of sacks/ha)") +
  guides(fill=guide_legend(title="Treatment")) +
  ggtitle("Rice Yield by Province", subtitle = "Wet Season, 2018") +
  labs(caption = "Source: Field verification testing results of carageenan plant food supplement (CPGP), DOST-Region 2") 
```





```{r}
cpgp %>%
  filter(season == "wet") %>%
  mutate(province = reorder(province, -CPGP)) %>%
  gather(group, yield, CPGP:Control) %>%
  ggplot(aes(province, yield, fill = group)) +
  geom_col(position = position_dodge(), alpha = 0.7, color = "black") +
  scale_fill_grey(start = 0.2, end = .7) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  xlab("Province") +
  ylab("Yield (no. of sacks/ha)") +
  guides(fill=guide_legend(title="Treatment")) +
  ggtitle("Rice Yield by Province", subtitle = "Wet Season, 2018") +
  labs(caption = "Source: Field verification testing results of carageenan plant food supplement (CPGP), DOST-Region 2") 
```


## Option 3

* Bars are arranged in decreasing order of percentage difference of yield in areas applied with carageenan over the yield in areas not applied with carageenan.
* One plot with two subplots (by season).

```{r}
cpgp2 <- cpgp %>%
  mutate(province.season = paste(province, season, sep = ".")) %>%
  mutate(province.season = factor(province.season, levels = province.season[order(pct)])) %>%
  mutate(season = case_when(season == "dry"~"Dry Season",
                            TRUE~"Wet Season"))
cpgp2 %>%
  ggplot(aes(province.season, pct)) +
  geom_col(alpha = 0.7, color = "black", width = 0.7) +
  scale_x_discrete(name = "Province", breaks = cpgp2$province.season, labels = cpgp2$province) +
  facet_wrap(~season, scales = "free") +
  coord_flip() +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  xlab("Province") +
  ylab("% Yield (in no. of sacks/ha)") +
  guides(fill=guide_legend(title="Treatment")) +
  ggtitle("Rice Yield Percentage Difference by Province across Seasons (2018)", subtitle = "Carageenan over Non-Carageenan Group") +
  labs(caption = "Source: Field verification testing results of carageenan plant food supplement (CPGP), DOST-Region 2") 
```


```{r}
shape <- readOGR(dsn = ".", layer = "Provinces")
```
```{r}
shape_df <- fortify(shape)
```

```{r, fig.height=6,fig.width=8}
shape_reg2 <- shape_df %>% filter(id %in% c(11,
 12,
 16,
 17,
 18,
 19,
 22,
 23,
 32,
 33,
 34,
 36,
 37,
 38,
 39,
  4,
 44,
 45,
 46,
 49,
 54,
 55,
 56,
 57,
 59,
 60,
76,
 7,
 78,
  9)) 

shape_reg2 <- shape_reg2 %>%
  mutate(pct = case_when(
    id == "7"~ 22.1,
    id == "9"~21.9,
    id == "78"~17.1,
    id == "76"~15.3,
    id == "16"~13.86,
    TRUE~NA_real_
  ))

map <- ggplot(data = shape_reg2, aes(x = long, y = lat, group = group))
map + geom_path() 
```

